---
title: "Part annotations preprocessing"
author: "Bria Long and Holly Huey"
date: "1/4/2022, updated 7/2023"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

This markdown was written for *kiddraw_annotations* (data originally collected in Long, Fan, Chai, & Frank, 2021). The data and figures of this markdown will be submitted to the CogSci conference 2022. 

Note about what happened before this markdown: 
1) data collected from the experiment through analysis/step2_generate_metadata/kiddraw_generate_metadata.ipynb

2) data was preprocessed in analysis/step3_analysis/kiddraw_analyses.ipynb — in particular, data sessions were excluded based on low accuracy on the catch trials and we used this notebook to check whether every drawing has responses from at least 3 annotators. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=FALSE, warning=FALSE)
```

```{r message = FALSE}
library(tidyverse)
library(lme4)
library(pander)
library(lmerTest)
library(ggthemes)
library(stringr)
library(tidytext) # for plotting
library(knitr) # for html rendering

```

# Preprocessing
## Load in all data and bind

```{r}
data_dir = here::here('data/drawing_annotations_raw/')
files = dir(data_dir)

file_count = 0
for (f in files){
  file_count = file_count+1
  data_chunk = read_csv(paste0(data_dir, f))
  if (file_count==1){
    all_data = data_chunk
  }
  else {
  all_data = full_join(all_data, data_chunk)
  }
}
```


```{r message = FALSE}
## how many total participants (after preprocessing/exclusions)?
total_annotators = length(unique(all_data$gameID))
```
```{r}
save(all_data, file = here::here('data/part_annotations_processed/all_data_agreed_or_not.Rdata'))
```


```{r}
 d <- all_data %>%
  #sessionID = of skethcer, gameID = prolific annotating ID
  select(roi_labelName, category, age, sessionID, gameID, catch, strokeIndex, filename, roi_buttonType, gameType, arcLength, svg) %>%
  filter(catch==FALSE) %>% # exclude catch trials
  mutate(age_numeric =
           as.numeric(str_split_fixed(age,'age',2)[,2]))  # make numeric version of age

```

##  Count number of images per age/category
```{r}
img_per_category_age <- d %>%
  group_by(category, age_numeric) %>%
  summarize(count_images = length(unique(filename)))  %>%
  mutate(category = factor(category, levels = c("bird", "fish", "rabbit","dog" ,"sheep","tiger" ,"camel" , "bear", "cup","lamp", "hat","bottle", "car", "boat","airplane","train")))

```

## Compute how many images we have more than two annotators
```{r}
d_agree <- d %>%
  group_by(filename) %>%
  mutate(count_participants = length(unique(gameID))) %>%
  filter(count_participants >= 2) 

length(unique(d_agree$filename))
```

```{r}
d_agree_3 <- d %>%
  group_by(filename) %>%
  mutate(count_participants = length(unique(gameID))) %>%
  filter(count_participants >= 3) 

length(unique(d_agree_3$filename))
```
## Look at agreement by label
```{r}
all_responses_by_age <- d %>%
  group_by(age_numeric) %>%
  count(roi_buttonType)
```

```{r}
##
d_check_agree <- d %>%
  group_by(filename) %>%
  mutate(roi_labelName = tolower(roi_labelName)) %>%
  mutate(count_participants = length(unique(gameID))) %>%
  filter(count_participants > 2) %>% # at least 2 participants
  add_count(filename, roi_labelName, strokeIndex, roi_buttonType)  %>%
  mutate(include = n>=(count_participants-1))

```

### Calculate agreement
```{r}
agree_by_age_by_class <- d_check_agree %>%
  group_by(category, age_numeric) %>%
  summarize(agree = mean(include)) 

agree_by_age <- d_check_agree %>%
  group_by (age_numeric) %>%
  summarize(agree = mean(include)) 

agree_by_category <- d_check_agree %>%
  group_by (category) %>%
  summarize(agree = mean(include)) 
```

### Plot agreements
```{R}
ggplot(data = agree_by_age_by_class, aes(x=age_numeric, y=agree, col=category)) +
  geom_point() +
  theme_few() +
  facet_wrap(~category) +
  xlab('Age of sketcher')
```




### Construct preprocessed data structure
```{r}
d_agree_labels <- d_check_agree %>%
  filter(include==TRUE) %>% # ibetween 66-80%
  select(-gameID, -catch, -sessionID) %>% 
  distinct() %>% # get rid of duplicate rows across annotators
  # Rename factor levels to be pretty
  mutate(game = factor(gameType, levels = c('big_animals','small_animals','vehicles','objects'), labels = c('Big Animals','Small Animals','Vehicles', 'Objects'))) %>%
  mutate(category = factor(category, levels = c("bird", "fish", "rabbit","dog" ,"sheep","tiger" ,"camel" , "bear", "cup","lamp", "hat","bottle", "car", "boat","airplane","train")))

# get rid of svg
d_agree_labels_with_svg <- d_check_agree %>%
  filter(include==TRUE) %>% # 
  select(-gameID, -catch, -sessionID) %>% 
  distinct() %>% # get rid of duplicate rows across annotators
  # Rename factor levels to be pretty
  mutate(game = factor(gameType, levels = c('big_animals','small_animals','vehicles','objects'), labels = c('Big Animals','Small Animals','Vehicles', 'Objects'))) %>%
  mutate(category = factor(category, levels = c("bird", "fish", "rabbit","dog" ,"sheep","tiger" ,"camel" , "bear", "cup","lamp", "hat","bottle", "car", "boat","airplane","train")))

d_agree_labels <- d_agree_labels %>%
  select(-svg)


```

```{r}
save(d_agree_labels, file = here::here('data/part_annotations_processed/merged_annotations.RData'))

save(d_agree_labels, file = here::here('data/part_annotations_processed/merged_annotations.csv'))
```
```{r}
pander(sessionInfo())
```
