---
title: "Drawing analyses: preprocess and merge datasets"
author: "Bria Long"
date: "7/2022, finalized 7/2023"
output:
  html_document:
    toc: true
    theme: united
---

# Libraries
```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(assertthat)
library(ggthemes)
library(viridis)
library(lme4)
library(lmerTest)
library(langcog)
library(pander)
```

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)

# Set random seed for reproducibility
set.seed(123)
```

## Load, describe, and join the datasets
### Filtered dataset metadata
```{r}
all_meta <- read_csv(file = here::here('data/drawings/stringent_cleaned_dataset_meta/all_object_metadata_cleaned.csv')) %>%
  as_tibble() %>%
  mutate(category = str_split_fixed(category,' ',2)[,2]) %>%
  mutate(category = str_replace(category,' ','.'))  # ice cream
```

### Basic descriptives of filtered set
```{r}
num_subs = length(unique(all_meta$session_id))
```

The final, filtered dataset of N=`r length(unique(all_meta$filename))`  drawings from `r length(unique(all_meta$category))` categories from `r num_subs` children who were on average `r mean(all_meta$age_numeric)` years of age (range 3-10 years). 

### Load category frequency ratings
```{r}
frequency = read_csv(file = here::here('data/surveys/drawing_experience/preprocessed/Category_frequency_survey.csv')) 
```

To assess this, `r length(unique(frequency$subject_id))` parents of children aged 3-10 years filled out a survey asking about the frequency with with their children drew the categories in the dataset.

```{r}
count_by_age <- frequency %>%
  group_by(childs_age) %>%
  dplyr::summarize(num_surveys = length(unique(subject_id)))
```

```{r}
freq_by_category <- frequency %>%
  # filter(childs_age > 2) %>%
  mutate(category = str_split_fixed(category,' ',2)[,2]) %>%
  mutate(category = str_replace(category,' ','.')) %>%
  filter(category %in% all_meta$category) %>%
  group_by(category) %>%
  summarize(drawing_frequency = mean(often_drawn_rating)) %>%
  mutate(above_median_freq = drawing_frequency > median(drawing_frequency)) 

write_csv(freq_by_category, here::here('data/surveys/drawing_experience/preprocessed/freq_by_category.csv'))


```

### Load tracing data
```{r}
all_tracings <- read_csv(here('data/tracing/rated_all_museumstation_filtered.csv'))%>%
  select(-...1, -X)

## Make averages for joining
by_subject_tracing_avg <- all_tracings %>%
  distinct(session_id, category, age, rating) %>% 
  group_by(session_id) %>%
  summarize(avg_tracing_rating = mean(rating))
```

```{r}
tracing_correlation <- all_tracings %>%
  distinct(session_id, category, age, rating) %>% 
  group_by(session_id) %>%
  mutate(num_tracings = length(unique(category))) %>%
  filter(num_tracings == 2) %>%
  select(session_id, category, rating) %>%
  pivot_wider(names_from = 'category', values_from = 'rating')

tracing_cor = cor.test(tracing_correlation$square, tracing_correlation$shape)
```

We found that tracing scores produced by the same participant were moderately correlated ($r$(6754) = .60, $t$ = 61.93,$p$ < .001, CI = [`tracing_cor$conf.int[1]`, `tracing_cor$conf.int[2]`], despite the irregular shape being harder to trace than the square.

### Load category animacy/size (hardcoding)
```{r}
animacy_csv <- read_csv(here::here('data/drawings/category_metadata/animacy.csv')) %>%
  as_tibble() %>%
  mutate(animacy_size = case_when(animacy == '0' & size=='0' ~ 2, # small objects
                                  animacy == '0' & size=='1' ~ 1, # big objects
                                  animacy == '1' & size=='0' ~ 4, # small animals
                                  animacy == '1' & size=='1' ~ 3)) # big animals

```

### Load CLIP classifications
```{r}
load(file=here::here('data/clip_outputs/fullset/clip_by_image.RData'))
load(file=here::here('data/clip_outputs/fullset/clip_long.RData'))

```


### Load VGG classification data
```{r}
num_batches=232
# reg_string = 'C_0.1_T_0.1'
reg_string = 'P1'

layers = c('P1','P2','P3','P4','P5','FC6','FC7')
for (this_layer in layers){
  
temp_class_data <- read.csv(here::here('data','compiled_classifications',paste0(this_layer,'batchtotal_', as.character(num_batches),'.csv'))) %>%
  mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>%
  mutate(image_name = paste(target_label,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X)  %>%
  mutate(category = str_replace(category,' ','.')) %>% # ice cream = ice.cream 
  mutate(layer = this_layer) 

  if (this_layer=='P1'){
    all_layer_class = temp_class_data
  }
  else {
  all_layer_class <- all_layer_class %>%
    full_join(temp_class_data)
  }

}
```


```{r}
## Order these layers reasonably.
layers_ordered = c('P1','P2','P3','P4','P5','FC6','FC7')

all_layer_class <- all_layer_class %>%
 mutate(layer = factor(layer, levels = layers_ordered)) %>%
 select(-X.1, -index, -batch, -batch_str) %>%
 rename(guessed_category = target_label)


```


#### For each layer
Save vgg layers outputs for extra analyses
```{r}
save(all_layer_class, file=here::here('data/compiled_classifications/vgg_outputs.RData'))
```


```{R}
# classification_data_fc7 <- read.csv(here::here('data','compiled_classifications/',paste0('C_0.1_T_0.1', 'batchtotal_',as.character(num_batches),'.csv'))) %>%
#   mutate(session_id = paste('cdm_',session_id,sep="")) %>%
#   mutate(age_numeric = age) %>%
#   mutate(age = paste('age',age,sep="")) %>%
#   mutate(age = as.factor(age)) %>%
#   mutate(category = target_label) %>%
#   mutate(image_name = paste(target_label,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
#   select(-X)  %>%
#   mutate(category = str_replace(category,' ','.'))  # ice cream = ice.cream

```

```{r}
# classification_data_fc6 <- read.csv(here::here('data','compiled_classifications/',paste0('FC6','batchtotal_',as.character(num_batches),'.csv'))) %>%
#   mutate(session_id = paste('cdm_',session_id,sep="")) %>%
#   mutate(age_numeric = age) %>%
#   mutate(age = paste('age',age,sep="")) %>%
#   mutate(age = as.factor(age)) %>%
#   mutate(category = target_label) %>%
#   mutate(image_name = paste(target_label,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
#   select(-X)  %>%
#   mutate(category = str_replace(category,' ','.'))  # ice cream = ice.cream

```


### Load part emphasis
```{r}
# all annotations before filtering
load(file = here::here('data/part_annotations_processed/merged_annotations.RData'))
```

```{r}
# preprocesssed emphasis data
load(file = here::here('data/part_annotations_processed/part_emphasis.RData'))
```

```{r}
# example drawing in presentation, or any other we want to examine
# example <- part_emphasis_all %>% filter(filename == 'bird_sketch_age8_cdm_run_v31530484377182.png')
# 
# what_annotations <- d_agree_labels %>% filter(filename == 'bird_sketch_age8_cdm_run_v31530484377182.png')
```

## Join meta data, drawing frequnecy, and classification data
```{r}
d <- all_layer_class %>% 
  filter(layer=='FC6') %>%
  gather(key = 'class', value = 'prob', contains('prob')) %>%
  mutate(class = str_split_fixed(class, '_prob',2)[,1]) %>%
  group_by(image_name, age, category, correct_or_not, session_id, age_numeric) %>%
  summarize(denom = sum(prob), target_label_prob = prob[class==category], log_odds = log(target_label_prob / (denom - target_label_prob))) %>%
  rename(filename = image_name) %>%
  left_join(all_meta, by=c("filename", "category", "age_numeric","session_id")) %>%
  mutate(draw_duration = draw_duration_old) %>% # using end of last stroke - end of first stroke (is 0 for one stroke drawings)
  mutate(run = substr(session_id,0,10)) %>% 
  left_join(freq_by_category) %>%
  mutate(correct_or_not = as.numeric(as.logical(correct_or_not)))

```


## Join tracing ratings
```{r}
d <- d %>%
  left_join(by_subject_tracing_avg)
```


### Asserts to check all the joins
```{r}
# weird things were happening with category matching, check
assert_that(length(unique(d$filename)) == length(unique(all_layer_class$image_name)))

# every drawing should have all of these, regardless
assert_that(sum(is.na(d$age_numeric))==0)
assert_that(sum(is.na(d$category))==0)
assert_that(sum(is.na(d$correct_or_not))==0)

missing_meta <- d %>%
  filter(is.na(num_strokes))

assert_that(length(missing_meta$filename)==0)
```

```{r}
## merged vgg classifications with meta
# save(d, file=here::here('data/preprocessed_data/merged_vgg_class_and_meta.RData'))

##
# write_csv(d, file=here::here('data/preprocessed_data/merged_vgg_class_and_meta.csv'))

```


# Merge CLIP classifications
```{R}
clip_by_image <- clip_long %>%
  mutate(category = str_replace(category,' ','.')) %>%
  mutate(guessed_category = str_replace(guessed_category,' ','.'))  %>%
  mutate(category = as.factor(category), guessed_category = as.factor(guessed_category)) %>%
  group_by(kid_age, session_id, category) %>%
  summarize(max_prob = max(prob), clip_category = guessed_category[prob == max_prob]) 

```

```{r}
# There are 695 drawings for which clip isn't sure between 2 options 
what <- clip_by_image %>%
  group_by(kid_age, session_id, category) %>%
  mutate(num_matches = length(clip_category)) %>%
  filter(num_matches > 1) 
```

Approach is to randomly sample one of those categories and then count that as correct.
```{r}
clip_by_image_better <- clip_long %>%
  rename(age_numeric = kid_age) %>%
  mutate(category = str_replace(category,' ','.')) %>%
  mutate(guessed_category = str_replace(guessed_category,' ','.'))  %>%
  group_by(session_id, category, age_numeric) %>%
  summarize(target_label_prob = prob[category==guessed_category], denom = sum(prob),  log_odds = log(target_label_prob / (denom - target_label_prob)), max_prob = max(prob), clip_category = guessed_category[prob == max_prob])  %>%
  mutate(correct_or_not = (clip_category == category)) %>%
  group_by(age_numeric, session_id, category) %>%
  sample_n(1) 

```


```{r}
d_clip <- clip_by_image_better %>% 
  mutate(session_id = paste0("cdm_", session_id)) %>%
  group_by(age_numeric, category, correct_or_not, session_id) %>%
  left_join(all_meta, by=c("category", "age_numeric","session_id")) %>%
  mutate(draw_duration = draw_duration_old) %>% # using end of last stroke - end of first stroke (is 0 for one stroke drawings)
  mutate(run = substr(session_id,0,10)) %>% 
  left_join(freq_by_category) %>%
  mutate(correct_or_not = as.numeric(as.logical(correct_or_not))) %>%
  left_join(by_subject_tracing_avg)


```

### Asserts to check all the joins
```{r}
# weird things were happening with category matching, check
# assert_that(length(unique(d_clip$filename)) == length(unique(all_layer_class$image_name)))

# every drawing should have all of these, regardless
assert_that(sum(is.na(d_clip$age_numeric))==0)
assert_that(sum(is.na(d_clip$category))==0)
assert_that(sum(is.na(d_clip$correct_or_not))==0)

missing_meta <- d_clip %>%
  filter(is.na(num_strokes))

assert_that(length(missing_meta$filename)==0)
```

```{r}
## merged clip classifications with meta
# save(d_clip, file=here::here('data/preprocessed_data/merged_clip_class_and_meta.RData'))

##
# write_csv(d_clip, file=here::here('data/preprocessed_data/merged_clip_class_and_meta.csv'))
```


# Session info
```{R}
pander(sessionInfo())
```

